[Re] On the coexistence of specialists and generalists

### 2017-10-16 article/Poisot-2017.tex
All figures done, some text in

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\usepackage{amssymb,amsmath,array,amsthm}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Georgios Detorakis,
  },
            pdftitle=
{
[Re] A Generalized Linear Integrate-and-Fire Neural Model Produces Diverse
Spiking Behaviors
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

% --- Document ----------------------------------------------------------------
\title{[Re] A Generalized Linear Integrate-and-Fire Neural Model Produces Diverse
Spiking Behaviors}

    \usepackage{authblk}
                        \author[1]{Georgios Detorakis}
                            \affil[1]{Department of Cognitive Sciences, UC Irvine, Irvine CA, USA}

\date{\vspace{-5mm}
      \sffamily \small \href{mailto:gdetorak@uci.edu (gdetor@protonmail.com)}{gdetorak@uci.edu (gdetor@protonmail.com)}}

@@

\begin{rebox}
\sffamily {\bfseries A reference implementation of}
\small
\begin{flushleft}
\begin{itemize}
    \item[→] A Generalized Linear Integrate-and-Fire Neural Model Produces Diverse
Spiking Behaviors, Stefan Mihalas and Ernst Niebur, Neural Computation
21, 704--718, 2009.
  \end{itemize}\par
\end{flushleft}
\end{rebox}

@@

Integrate-and-fire neurons are being used extensively in the field of
neuroscience for modeling spiking behaviors~\autocite{dayan:2001}. In
this work we provide a reference implementation
of~\autocite{mihalas:2009}, where the authors have introduced a
generalization of the leaky integrate-and-fire neuron model. The
Mihalas-Niebur Neuron (MNN) model is a linear integrate-and-fire neuron
model capable of expressing a rich spiking behavior based on a set of
parameters.

An MNN model expresses tonic and phasic spiking, class \(1\) and \(2\),
spike frequency adaptation, accommodation, threshold variability,
rebound spike, integrator, input bistability, hyperpolarizing spiking
and bursting, tonic, phasic and rebound bursting, mixed mode,
afterpotentials, basal bistability, preferred frequency and spike
latency. Due to its simplicity, the MNN model has been used in
neuromorphic implementations such as~\autocite{folowosele:2011}.

The model consists of linear differential equations, which describe the
membrane and threshold potentials and internal currents. All the results
provided in \autocite{mihalas:2009} have been obtained by using only two
internal currents and thus we use the exact same number of internal
currents in this work. The subthreshold dynamics are defined by a set of
linear ordinary differential equations, while an instantaneous threshold
potential controls when the neuron fires an action potential (spike) in
a dynamic way. The ability of the MNN model to generate such a diverse
spiking behavior is due to the complex update rules. In this work the
MNN model has been implemented in Python (version 3.6.1) using Numpy
(version 1.13.1) and Matplotlib (version 2.0.2) packages.

@@

In order to implement the model described in \autocite{mihalas:2009}, we
discretized the dynamical system using the forward Euler integration
scheme. The time step is fixed to \(0.1\, \mathrm{ms}\) for all the
simulations, and the total simulation time \(t_f\) varies according to
figure 1 of the original paper. Our implementation differs from the one
in the original paper, since in \autocite{mihalas:2009}, authors
numerically solve equation \(3.5\) (algebraic equation) under the
constraint imposed by inequality \(3.4\) and thus they compute the spike
times. On the other hand, in this work we directly compute numerically
the solution of the dynamical system defined by equations \(2.1\) and
\(2.2\) in \autocite{mihalas:2009} (see tables~~\ref{tbl:2}
and~~\ref{tbl:3}).

We provide all equations and parameters of the model in tables as it has
been suggested by~\autocite{nordlie:2009}. Table~~\ref{tbl:1} provides
the summary of the model. Tables~~\ref{tbl:2} and~~\ref{tbl:3} give the
subthreshold dynamics (differential equations) describing the membrane
and the threshold potentials as well as the two internal currents and
the update rules. The parameters for all the simulations are given in
table~~\ref{tbl:4}, while the external current intensities and pulse
duration are provided in table~~\ref{tbl:5}. The parameters in this work
are exactly the same used in the original paper (table 1, pg. \(711\)).
We had to infer the time intervals and the total simulation times for
the pulses since they are not given explicitly in the original paper.
Thus, we extracted the time intervals from figure \(1\) of
\autocite{mihalas:2009} by visual inspection. The initial conditions are
given in table~~\ref{tbl:6}.

All simulations ran on a Dell OptiPlex \(7040\), equipped with a sixth
generation i\(7\) processor, \(16\, \mathrm{GB}\) of physical memory and
running Arch Linux (x\(86\_64\)). The total execution time of all
simulations was \(2.41\) seconds and the peak consumed memory was
\(162\, {\mathrm{MB}}\)\footnote{Python memory profiler used
  (\url{https://pypi.python.org/pypi/memory_profiler}).}.

\hypertarget{tbl:1}{}
\begin{longtable}[]{@{}ll@{}}
\caption{\label{tbl:1}\textbf{Summary of the model.} }\tabularnewline
\toprule
Model Summary &\tabularnewline
\midrule
\endfirsthead
\toprule
Model Summary &\tabularnewline
\midrule
\endhead
Populations & No population -- single neuron model\tabularnewline
Topology & --\tabularnewline
Connectivity & --\tabularnewline
Neuron Model & Linear Integrate-and-Fire Neuron\tabularnewline
Channel Models & Linear, first order ODEs\tabularnewline
Synapse Model & --\tabularnewline
Plasticity & --\tabularnewline
Input & Constant current/rectangular pulses\tabularnewline
Measurements & Membrane potential, phase plane\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{tbl:2}{}
\begin{longtable}[]{@{}ll@{}}
\caption{\label{tbl:2}Description of the subthreshold dynamics of
Mihalas--Niebur neuron model. \(V(t)\) and \(\Theta(t)\) are the
membrane and threshold potentials, respectively. \(E_L\) and
\(\Theta_{\infty}\) are the reversal potentials for the membrane and
threshold variables, respectively. \(a, b, k_1, k_2\) and \(G\) are
constant parameters. \(I_e\) is the external current applied on the
neuron model. }\tabularnewline
\toprule
Neuron Model &\tabularnewline
\midrule
\endfirsthead
\toprule
Neuron Model &\tabularnewline
\midrule
\endhead
Name & Mihalas-Niebur Neuron (MNN)\tabularnewline
Type & Linear Leaky Integrate-and-Fire Neuron\tabularnewline
Membrane Potential &
\( \frac{\mathrm{d}V(t)}{\mathrm{d}t} = \frac{1}{C} \Big(I_e + I_1 + I_2 - G(V(t) - E_L)  \Big) \)\tabularnewline
Instantaneous Threshold Potential &
\( \frac{\mathrm{d}\Theta(t)}{\mathrm{d}t} = a(V(t) - E_L) - b(\Theta(t) - \Theta_{\infty}) \)\tabularnewline
Internal Currents &
\( \frac{\mathrm{d}I_{1}(t)}{\mathrm{d}t} = -k_1I_1(t) \)\tabularnewline
&
\( \frac{\mathrm{d}I_{2}(t)}{\mathrm{d}t} = -k_2I_2(t) \)\tabularnewline
\bottomrule
\end{longtable}

\pagebreak

\hypertarget{tbl:3}{}
\begin{longtable}[]{@{}ll@{}}
\caption{\label{tbl:3}\textbf{Update rules.} \(V_r\) and \(\Theta_r\)
are the reset values for the membrane and threshold potentials,
respectively. \(R_1, R_2, A_1\) and \(A_2\) are constants.
}\tabularnewline
\toprule
Variable & Rule\tabularnewline
\midrule
\endfirsthead
\toprule
Variable & Rule\tabularnewline
\midrule
\endhead
\(V(t)\) & \(V_r\)\tabularnewline
\(\Theta(t)\) & \(\max\{\Theta_r, \Theta(t) \}\)\tabularnewline
\(I_1(t)\) & \(R_1 \times I_1(t) + A_1\)\tabularnewline
\(I_2(t)\) & \(R_2 \times I_2(t) + A_2\)\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{tbl:4}{}
\begin{longtable}[]{@{}lllll@{}}
\caption{\label{tbl:4}\textbf{Simulation Parameters}. Common parameters
for all simulations: \(b = 10\, \mathrm{s^{-1}}\),
\(G/C = 50\, \mathrm{s^{-1}}\), \(k_1 = 200\, \mathrm{s^{-1}}\),
\(k_2 = 20\, \mathrm{s^{-1}}\),
\(\Theta_{\infty} = -0.05\, \mathrm{V}\), \(R_1 = 0\), \(R_2 = 1\),
\(E_l = -0.07\, \mathrm{V}\), \(V_r = -0.07\, \mathrm{V}\),
\(\Theta_r = -0.06\, \mathrm{V}\). }\tabularnewline
\toprule
Figure & \(a (\mathrm{s^{-1}})\) & \(\frac{A_1}{C} (\mathrm{V/s})\) &
\(\frac{A_2}{C} (\mathrm{V/s})\) & \(t_f \mathrm{s}\)\tabularnewline
\midrule
\endfirsthead
\toprule
Figure & \(a (\mathrm{s^{-1}})\) & \(\frac{A_1}{C} (\mathrm{V/s})\) &
\(\frac{A_2}{C} (\mathrm{V/s})\) & \(t_f \mathrm{s}\)\tabularnewline
\midrule
\endhead
1A & \(0\) & \(0\) & \(0\) & \(0.2\)\tabularnewline
1B & \(0\) & \(0\) & \(0\) & \(0.5\)\tabularnewline
1C & \(5\) & \(0\) & \(0\) & \(0.2\)\tabularnewline
1D & \(5\) & \(0\) & \(0\) & \(0.5\)\tabularnewline
1E & \(5\) & \(0\) & \(0\) & \(1.0\)\tabularnewline
1F & \(5\) & \(0\) & \(0\) & \(0.4\)\tabularnewline
1G & \(5\) & \(0\) & \(0\) & \(1.0\)\tabularnewline
1H & \(5\) & \(0\) & \(0\) & \(0.3\)\tabularnewline
1I & \(5\) & \(0\) & \(0\) & \(0.4\)\tabularnewline
1J & \(5\) & \(0\) & \(0\) & \(1.0\)\tabularnewline
1K & \(30\) & \(0\) & \(0\) & \(0.4\)\tabularnewline
1L & \(30\) & \(10\) & \(-0.6\) & \(0.4\)\tabularnewline
1M & \(5\) & \(10\) & \(-0.6\) & \(0.5\)\tabularnewline
1N & \(5\) & \(10\) & \(-0.6\) & \(0.5\)\tabularnewline
1O & \(5\) & \(10\) & \(-0.6\) & \(1.0\)\tabularnewline
1P & \(5\) & \(5\) & \(-0.3\) & \(0.5\)\tabularnewline
1Q & \(5\) & \(5\) & \(-0.3\) & \(0.2\)\tabularnewline
1R & \(0\) & \(8\) & \(-0.1\) & \(0.2\)\tabularnewline
1S & \(5\) & \(-3\) & \(0.5\) & \(0.8\)\tabularnewline
1T & \(-80\) & \(0\) & \(0\) & \(0.05\)\tabularnewline
\bottomrule
\end{longtable}

\pagebreak

\hypertarget{tbl:5}{}
\begin{longtable}[]{@{}lll@{}}
\caption{\label{tbl:5}\textbf{External current}. This table provides the
external current for each panel in Figure~~\ref{fig:1}. There are two
types of external currents, constants and pulses. In the case of pulses
the duration of each pulse is given in seconds along with its intensity.
}\tabularnewline
\toprule
Figure & Type & \(I_e/C (V/s)\)\tabularnewline
\midrule
\endfirsthead
\toprule
Figure & Type & \(I_e/C (V/s)\)\tabularnewline
\midrule
\endhead
1A & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(1.5\)\tabularnewline
1B & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(1 + 10^{-6}\)\tabularnewline
1C & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(2\)\tabularnewline
1D & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(1.5\)\tabularnewline
1E & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(1.5 (0.1 \mathrm{s}),\, 0 (0.5\mathrm{s}),\, 0.5 (0.1\mathrm{s}),\, 1 (0.1\mathrm{s}),\, 1.5 (0.1\mathrm{s}),\, 0 (0.1 \mathrm{s}) \)\tabularnewline
1F & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(1.5 (0.02 \mathrm{s}),\, 0 (0.18 \mathrm{s}),\, -1.5 (0.025 \mathrm{s}),\, 0 (0.025 \mathrm{s}),\, 1.5 (0.025 \mathrm{s}),\, 0 (0.125 \mathrm{s})\)\tabularnewline
1G & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(0 (0.05 \mathrm{s}),\, -3.5 (0.756 \mathrm{s}),\, 0 (0.194 \mathrm{s}) \)\tabularnewline
1H & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\( 2(1 + 10^{-6}) \)\tabularnewline
1I & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\( 1.5 (0.02 \mathrm{s}),\, 0 (0.01 \mathrm{s}),\, 1.5 (0.02 \mathrm{s}),\, 0 (0.25 \mathrm{s}),\, 1.5 (0.02 \mathrm{s}),\, 0 (0.02 \mathrm{s})\)\tabularnewline
& & \( 1.5 (0.02 \mathrm{s}),\, 0 (0.04 \mathrm{s}) \)\tabularnewline
1J & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\( 1.5 (0.1 \mathrm{s}),\, 1.7 (0.4 \mathrm{s}),\, 1.5 (0.1 \mathrm{s}),\, 1.7 (0.4 \mathrm{s}) \)\tabularnewline
1K & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(-1\)\tabularnewline
1L & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(-1\)\tabularnewline
1M & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(2\)\tabularnewline
1N & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(1.5\)\tabularnewline
1O & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(0 (0.1 \mathrm{s}),\, -3.5 (0.5 \mathrm{s}),\, 0 (0.4 \mathrm{s})\)\tabularnewline
1P & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(2\)\tabularnewline
1Q & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(2 (0.015 \mathrm{s}),\, 0 (0.185 \mathrm{s})\)\tabularnewline
1R & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(5 (0.01 \mathrm{s}),\, 0 (0.09 \mathrm{s}),\, 5 (0.01 \mathrm{s}),\, 0 (0.09 \mathrm{s})\)\tabularnewline
1S & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(5 (0.005 \mathrm{s}),\, 0 (0.005 \mathrm{s}),\, 4 (0.005 \mathrm{s}),\, 0 (0.385 \mathrm{s}),\, 5 (0.005 \mathrm{s}),\, 0 (0.045 \mathrm{s}) \)\tabularnewline
& & \(4 (0.005\mathrm{s}),\, 0 (0.345 \mathrm{s}) \)\tabularnewline
1T & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(8 (0.002 {\mathrm{s}}),\, 0 (0.048 \mathrm{s})\)\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{tbl:6}{}
\begin{longtable}[]{@{}ll@{}}
\caption{\label{tbl:6}\textbf{Initial Conditions} In all simulations the
same initial conditions have been used, except from the one illustrated
in Figure ~\ref{fig:1} H. }\tabularnewline
\toprule
Variable & Initial Value\tabularnewline
\midrule
\endfirsthead
\toprule
Variable & Initial Value\tabularnewline
\midrule
\endhead
\(V(t)\) & \(-0.07\, \mathrm{V}\) / \(-0.03\, \mathrm{V}\) (Figure
1H)\tabularnewline
\(\Theta(t)\) & \(-0.05\, \mathrm{V}\) / \(-0.03\, \mathrm{V}\) (Figure
1H)\tabularnewline
\(I_1(t)\) & \(0.01\, \mathrm{V}\)\tabularnewline
\(I_2(t)\) & \(0.001\, \mathrm{V}\)\tabularnewline
\bottomrule
\end{longtable}

@@

All three figures from the original article have been successfully
replicated. All the different spiking behaviors of the model are
illustrated in Figure~~\ref{fig:1}, where the black solid line indicates
the membrane potential (\(V(t)\)), the red dashed line illustrates the
instantaneous threshold potentials (\(\Theta(t)\)), and the gray line
shows the input to the neuron (\(I_e/C\)). The \(x\)-axis scales in all
panels are exactly the same as in the original paper (indicating the
total simulation time (\(t_f\)), while the \(y\)-axis scale differs from
the one in the original paper. In this work the \(y\)-axis scale is the
same for all the subplots (\([-95, -25]\, {\mathrm{mV}}\)), except for
panels G and O (\([-145, -25]\, {\mathrm{mV}}\)).

Figures~~\ref{fig:2} and~~\ref{fig:3} depict the phase space of the
phasic spiking (\(V(t)\) and \(\Theta(t)\)) and phasic bursting
(\(V(t)\), \(I_1(t)\), and \(I_2(t)\)). In both figures the blue curves
and the black dots indicate the trajectory of the system and spike
events, respectively. In Figure~~\ref{fig:2} the gray arrows show the
evolution of the system (vector field of the system).
Figure~~\ref{fig:3} has a different orientation from the original one
but both the original figure and the replicated one illustrate the same
trajectories and spike events of the system. All the figures express the
same qualitative behavior as the original figures
in~\autocite{mihalas:2009}.

\begin{figure}
\centering
\includegraphics{figs/Figure01.pdf}
\caption{\textbf{Neural responses of MNN.} Black solid lines indicate
the membrane potential (\(V(t)\)), the red dashed lines show the
threshold potentials (\(\Theta(t)\)), and the gray lines the external
currents applied on each case. {\textbf{A}} tonic spiking, {\textbf{B}}
class \(1\), {\textbf{C}} spike frequency adaptation, {\textbf{D}}
phasic spiking, {\textbf{E}} accommodation, {\textbf{F}} threshold
variability, {\textbf{G}} rebound spike, {\textbf{H}} class \(2\),
{\textbf{I}} integrator, {\textbf{J}} input bistability, {\textbf{K}}
hyperpolarization induced spiking, {\textbf{L}} hyperpolarization
induced bursting, {\textbf{M}} tonic bursting, {\textbf{N}} phasic
bursting, {\textbf{O}} rebound burst, {\textbf{P}} mixed mode,
{\textbf{Q}} afterpotentials, {\textbf{R}} basal bistability,
{\textbf{S}} preferred frequency, {\textbf{T}} spike
latency.}\label{fig:1}
\end{figure}

\begin{figure}
\centering
\includegraphics{figs/Figure02.pdf}
\caption{\textbf{Phase space of phasic spiking.} Blue solid lines
indicate the trajectories of the model in the phase spiking behavior
(Figure~~\ref{fig:1} D). The dashed line corresponds to
\(V(t) =  \Theta(t)\), and the black dots represent spike events. The
parameters for this simulation are the same as in Figure~~\ref{fig:1}
D.}\label{fig:2}
\end{figure}

\begin{figure}
\centering
\includegraphics{figs/Figure03.pdf}
\caption{\textbf{Phase space of phasic bursting.} Blue solid lines
represent the trajectories of the system and the black dots indicate
spiking events. The parameters for this simulation are the same as in
Figure~~\ref{fig:1} N.}\label{fig:3}
\end{figure}

@@

All figures in~\textcite{mihalas:2009} have been successfully replicated
with high fidelity. Overall, the whole reproducing process was smooth
and without obscure points since most of the parameters are provided in
the original article. Only the time intervals for which the external
current is applied to the model and the initial conditions are not
provided explicitly. Therefore, we had to extract that information from
figure \(1\) of the original article. To conclude, the
article~\autocite{mihalas:2009} has been successfully reproduced without
any discrepancy.

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Timothée Poisot,
  },
            pdftitle=
{
[Re] On the coexistence of specialists and generalists
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

% --- Document ----------------------------------------------------------------
\title{[Re] On the coexistence of specialists and generalists}

    \usepackage{authblk}
                        \author[1]{Timothée Poisot}
                            \affil[1]{Département de Sciences Biologiques, Université de Montréal, Montréal,
QC, Canada}

\date{\vspace{-5mm}
      \sffamily \small \href{mailto:timothee.poisot@umontreal.ca}{timothee.poisot@umontreal.ca}}

@@

\begin{rebox}
\sffamily {\bfseries A reference implementation of}
\small
\begin{flushleft}
\begin{itemize}
    \item[→] On the coexistence of specialists and generalists, David Sloan Wilson
and Jin Yoshimura, The American Naturalist 144:4, 692-707, 1994.
  \end{itemize}\par
\end{flushleft}
\end{rebox}

@@

The coexistence of specialists and generalist within ecological
communities is a long-standing question. \textcite{wils94csg} have
suggested that this coexistence can be understood when examined in the
light of (i) differential fitness loss associated to specialism, (ii)
active habitat selection, (iii) negative density dependence due to
competition, and (iv) stochastic changes in habitat quality, that allow
combinations of species to persist even though coexistence would not be
possible in a purely deterministic world. Here I propose an
implementation of this model in \emph{Julia} \autocite{beza17jfa}, and
show that it is able to reproduce most figures from the original
manuscript.

@@

The \textcite{wils94csg} model describes three species across two
patches of habitat. Species 1 is a specialist of habitat 1, species 2 is
a specialist of habitat 2, and species 3 is a generalist. This results
in the maximum density that these species can reach in both habitats:

\begin{equation}
\mathbf{K} = \begin{bmatrix}
  K_1 & aK_1 \\
  a_K2 & K_2 \\
  bK_1 & b_K2
\end{bmatrix} \,.
\end{equation}

In this matrix, \(K_1\) is the quality of habitat 1, \(K_2\) is the
quality of habitat 2, \(a\) is the fitness cost of the specialist in its
non-optimal environment, and \(b\) is the fitness cost of generalism.
Note that \(1 > b > a > 0\).

Species distribute themselves across habitats in a way that minimizes
the negative effect of other species on their fitness. This is modelled
by each species having a value \(p_i\), which is the proportion of its
species choosing habitat 1. Values of \(\mathbf{p}\) are found by
measuring the negative density effect of each species in each habitat:

\begin{equation}
D_{l1} = \frac{\sum_{i\in l,m,m}p_iN_i}{K_{l1}}
\end{equation}

and

\begin{equation}
D_{l2} = \frac{\sum_{i\in l,m,m}(1-p_i)N_i}{K_{l1}} \,.
\end{equation}

The value of \(p_l\) for which \(D_{l1}=D_{l2}\) is

\begin{equation}
p_l = - \frac{(K_{l1}+K_{l2})(N_mp_m+N_np_n)-K_{l1}(N_l+N_m+N_n)}{N_l(K_{l1}+K_{l2})} \,.
\end{equation}

We fix \(p_m\) and \(p_n\), and find the value of \(p_l\), while
enforcing the constraint of \(0 \leq p_l \leq 1\). Repeating this
procedure a few times for the different species yields the optimal
values of \(\mathbf{p}\); we can measure the density of individuals in
both habitats. Before we do so, there is a proportion \(g\) of
individuals that select habitats at random. Given a total population
size of \(N_i\), there are \(N_i(g/2)\) individuals will go to either
habitat, and \(N_i(1-g)p_i\) will pick habitat 1. With this information,
we can write the matrix describing habitat selection:

\begin{equation}
\mathbf{N} = \begin{bmatrix}
  N_1(\frac{g}{2}+(1-g)p_1) & N_1(\frac{g}{2}+(1-g)(1-p_1))\\
  N_2(\frac{g}{2}+(1-g)p_2) & N_2(\frac{g}{2}+(1-g)(1-p_2))\\
  N_3(\frac{g}{2}+(1-g)p_3) & N_3(\frac{g}{2}+(1-g)(1-p_3))
\end{bmatrix} \,.
\end{equation}

Finally, the fitness of every species in each habitat is given by

\begin{equation}
W_{ij} = \text{exp}\left[r\left(1-\frac{N_{i1}+N_{i2}+N_{i3}}{K_{ij}}\right)\right] \,,
\end{equation}

where \(r\) is the growth rate (assumed equal). The population size at
the next timestep is simply given by

\begin{equation}
\mathbf{N}_{t+1} = \mathbf{W}\odot \mathbf{N}_{t} \,,
\end{equation}

where \(\odot\) is the element-wise multiplication.

@@

Original sources were not available, and no attempts were made to
contact the authors. For some non-stochastic situations, it is possible
to calculate expected values by hand. The original manuscript does
provide some of these values, and they were used to test this
implementation. Figure 2A and 2B in the original manuscript provide a
good diagnostic value, as they are based on non-stochastic situations.
In \textcite{fig:02},

\begin{figure}
\centering
\includegraphics{figure02.pdf}
\caption{Population dynamics and habitat preference of the generalist
alone (left), and following invasion by the two specialists at the
generalist equilibrium (right).}\label{fig:02}
\end{figure}

Results should be compared with original results and you have to explain
why you think they are the same or why they may differ (qualitative
result vs quantitative result). Note that it is not necessary to redo
all the original analysis of the results.

@@

Conclusion, at the very minimum, should indicate very clearly if you
were able to replicate original results. If it was not possible but you
found the reason why (error in the original results), you should exlain
it.

\begin{longtable}[]{@{}llllll@{}}
\caption{Table caption \{\#tbl:table\}}\tabularnewline
\toprule
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Heading 1\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Heading 2\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Heading 1\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Heading 2\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\midrule
\endhead
cell1 row1 & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 &
cell6 row 1\tabularnewline
cell1 row2 & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 &
cell6 row 2\tabularnewline
cell1 row3 & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 &
cell6 row 3\tabularnewline
\bottomrule
\end{longtable}

A reference to table \textcite{tbl:table}. A reference to figure
\textcite{fig:logo}. A reference to equation \textcite{eq:1}. A
reference to citation \textcite{markdown}.

\begin{figure}
\centering
\includegraphics{rescience-logo.pdf}
\caption{Figure caption}\label{fig:logo}
\end{figure}

\[ A = \sqrt{\frac{B}{C}} \] \{\#eq:1\}
